Project Ideas and Notes

### 2024-05-02 corridor_docs/ideas/thesis_ideas.Rmd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(citr)
```
insert_citation
### *Notes from conversation with Julian:*

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(citr)
```
insert_citation

Post SRS Badging ideas
1. Camera monitoring - Big mammals
2. Matrix densities
3. Go through John Orrock’s unpublished data
Other stuff to figure out
1. Housing
2. Funding
3. Steering committee questions

### *Notes from conversation with Julian:*
